Biotic invasions fuck with the manageability of pollination networks

### 2017-02-17 paper/supp_info_2.Rmd
Fix figure names, numbers and format

---
title: "Biotic invasions fuck with the manageability of pollination networks"
subtitle: "Supporting Information"
classoption: a4paper
csl: ecology-letters.csl
output:
  pdf_document:
    fig_crop: no
    keep_tex: yes
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{rotating}
- \renewcommand{\figurename}{Supporting Figure}
- \renewcommand{\tablename}{Supporting Table}
documentclass: artikel1
bibliography: references.bib
nocite: | 
  @Lopezaraiza-Mikel2007, @Bartomeus2008
---

@@

@@

@@

		names_fancy <- sp_names_fancy
		names_fancy[igraph::V(bi_net)$name %in%
																ends(bi_net, as_all_mat[[x]])[, 1]] <-
			sp_names_fancy_b[igraph::V(bi_net)$name %in%
																ends(bi_net, as_all_mat[[x]])[, 1]]

@@

We start with a directed network in which the direction of the link represents the direction of control (Supporting figure 1a). We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links (Supporting figure 1b). Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node in the left hand side is connected to at most one node in the right hand side. To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. Once we have the matching shown in the Supporting Figure 1b, it is then easy to identify the roles of each node in this representation: nodes on the right hand side that are connected to a matched link (purple) are matched, while those connected to a matched link on the left hand side are superior. This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Supporting Figure 1c). Supporting Figure 1d, e, and f ilustrate this approach for a network with bidirectional links.

@@

# par(mfrow=c(2,3), mar= c(0,0,0,0))
layout(matrix(c(1,2,3,4, 5, 6, 7, 7, 7), 3, 3, byrow = TRUE),
  	heights=c(8,8,1))
par( mar=c(0,0,0,0))
# ASYMMETRY
as_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 35,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma)

text(label_pos_x, label_pos_y, "a)", adj = c(0,0))

@@

bi_as_net %>%
	plot(layout = matrix(c(rep(c(-0.5, 0.9), each = 5), rep(seq(-0.8, 0.8, length.out = 5), 2)), ncol = 2), 
			 # vertex.size = igraph::V(.)$superior,
			 vertex.size = 30, 
			 vertex.label = c(bi_sp_names_fancy[6:10], bi_sp_names_fancy[1:5]),
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 # vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
			 # vertex.color = pal[igraph::V(.)$matched],
			 vertex.color = NA,
			 edge.color = pal[E(.)$matched],
			 edge.label = NA, 
			 edge.width = E(.)$matched/2,
			 edge.label.family = fam,
			 edge.label.color = igraph::E(.)$matched,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma, 
			 rescale = F)

text(-0.95, 0.825, "b)", adj = c(0,0))

@@

@@

@@

		names_fancy <- sp_names_fancy
		names_fancy[igraph::V(as_net)$name %in%
																ends(as_net, as_all_mat[[1]])[, 1]] <-
			sp_names_fancy_b[igraph::V(as_net)$name %in%
																ends(as_net, as_all_mat[[1]])[, 1]]

@@

		as_net %>% 
			plot(layout = lay, 
					 vertex.size = igraph::V(.)$superior * 10 + 20,
					 vertex.label = names_fancy,
					 vertex.label.family = fam,
					 vertex.label.color = l_c,
					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
					 # vertex.shape = igraph::V(.)$vertex.shape,
					 vertex.color = pal[igraph::V(.)$matched],
					 edge.color = pal[E(.)$matched],
					 edge.label = NA, 
					 edge.width = E(.)$matched/2,
					 edge.label.family = fam,
					 edge.label.color = igraph::E(.)$matched,
					 edge.label.cex = l_s,
					 edge.curved = F,
					 edge.arrow.size = 0.5,
					 margin = ma) %>% 
			print()

text(label_pos_x, label_pos_y, "c)", adj = c(0,0))

bi_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 35,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = T,
			 edge.arrow.size = 0.5,
			 margin = ma)
text(label_pos_x, label_pos_y, "d)", adj = c(0,0))

@@

@@

bi_bi_net %>%
	plot(layout = matrix(c(rep(c(0.9,-0.5), each = 5), rep(seq(-0.8, 0.8, length.out = 5), 2)), ncol = 2), 
			 # vertex.size = igraph::V(.)$superior,
			 vertex.size = 30,
			 vertex.label = bi_sp_names_fancy, 
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 # vertex.color = pal[igraph::V(.)$matched],
			 vertex.color = NA, 
			 edge.color = pal[igraph::E(.)$matched],
			 # edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.width = E(.)$matched/2,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin =  ma, 
			 # asp = 0.5, 
			 rescale = F)

text(-0.95, 0.825, "e)", adj = c(0,0))

nets[[1]]$bi_net %>%
	plot(layout = lay, 
			 vertex.label = nets[[1]]$names_fancy,
			 vertex.size = igraph::V(.)$superior * 10 + 20,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 vertex.color = pal[igraph::V(.)$matched],
			 edge.color = pal[igraph::E(.)$matched],
			 # edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = T,
			 edge.arrow.size = 0.5,
			 edge.width = E(.)$matched/2,
			 margin = ma, 
			 # asp = 0.5, 
			 rescale = T)

text(label_pos_x, label_pos_y, "f)", adj = c(0,0))

## LEGEND 
plot.new()
legend(0.16, 0.9, legend = c("unmatched link", "matched link"), horiz = TRUE,
			 lty = 1, 
			 col = pal[c(2, 4)],
			 lwd = 2, cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")

legend(0.57, 0.9, legend = c("unmatched node", "matched node"), horiz = TRUE,
			 pch = 21, 
			 pt.bg = pal[c(2, 4)],
			 pt.cex = 2,
			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")

legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("  superior node"))), horiz = TRUE,
			 pch = 21, 
			 # pt.bg = pal[c(2, 4)],
			 pt.cex = c(3),
			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
```

The algorithm implemented in `max_bipartite_matching`, however, is only able to find **one** of the, possibly many, maximum matchings in a network. One maximum matching is sufficient to calculate *n~D~* and hence to provide indication of a communitie's manageability, however it is not possible to estimate the role of individual species. To do that we need to calculate all possible maximum matchings (or all maximal cardinality matchings in weighted networks like ours). We start from the alternative bipartite representation in Supporting Figure 1b and assign an identity to each of the links in the network (shown as numbers in Supporting Figure 2a). We will call this bipartite representation *B*. We then construct the line graph of the alternative bipartite representation *L(B)* (Supporting Figure 2b). Each node in *L(B)* represents a link in *B* and are connected to each other only if they share a common node in *B*. We calculate the complement graph of *L(B)* and idetify all the maximum cliques (Supporting Figure 2c). Here some extra definitions are neccessary. First, the complement of *L(B)*, *H*, is a graph with the same nodes as *L(B)* but that has a link between two given nodes if and only if there is not a link in *L(B)*. Second, a clique is a subset of nodes such that any two of them are linked. Lastly, a maximum clique is a clique such that there are no cliques with more nodes. In this example there are two maximum cliques: that one formed by 1, 3 and 5, and by 2, 3 and 5. The final step is then to map these cliques into the original network to obtain all possible maximum cardinality matchings as shown in Figure 1 in the main text.

@@

text(-1, 1, "a)", adj = c(0,0))

@@

text(-1, 1, "b)", adj = c(0,0))

@@

text(-1, 1, "c)", adj = c(0,0))

@@

In the main text we show all maximum cardinality matchings for a simple example network. To further ilustrate our methodology, here we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Supporting Table 1; Supporting Figure 3). The largest component of this network is composed by 16 species of which 2 are non-invasive plants and the rest are pollinators. The one-to-one relationship between matched and superior nodes implies that in order to achieve full network controllability, most pollinators would be unmatched, and hence driver species that require external intervention. At the same time, both plants in the community, *Heracleum sphpndylum* and *Rubus fructicosus* and one of the pollinators *Orthotylus/Lygocorus* tend to be classified as superior nodes.

```{r fig-SA_exp, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 6.2, results = "hide", fig.cap = "**Illustration of the procedure with one empirical network**. (a) The initial visitation network. (b) The directed network in which the direction of control and the magnitude of the asymmetry are determined based on the mutual dependences. (c) One of the possible maximum matchings calculated using the procedures illustrated in the Supporting Figure 1 and 2."}
par(mfrow=c(2,2), mar=c(0,0,0,0))
n <- keep_largest_component(net$SA_exp)
replace_names <- data.frame(sp_name = igraph::V(n)$name) %>%
	dplyr::mutate(sp_number = 1:nrow(.),
								sp_letter = letters[sp_number], 
								sp_name = stringr::str_replace(sp_name, "[0-9]", ""),
								sp_name = stringr::str_replace(sp_name, "\\?rutitarse", "rufitarse"))
set.seed(7)

la <- igraph::layout_nicely(n)
n %>%
	plot(vertex.color = v_c, 
			 vertex.size = 15,
			 vertex.label = replace_names$sp_letter,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 vertex.label.cex = 0.9,
			 edge.label = round(igraph::E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s*0.8,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma, 
			 layout = la)
text(label_pos_x, label_pos_y, paste0(letters[1], ")"), adj = c(0,0))

@@

text(label_pos_x, label_pos_y, paste0(letters[2], ")"), adj = c(0,0))

@@

		igraph::V(as_net)$matched <- 2
		igraph::V(as_net)$matched[igraph::V(as_net)$name %in%
																ends(as_net, as_all_mat[[x]])[, 2]] <- 4

@@

@@

		as_net %>% 
			plot(layout = la, 
					 vertex.size = igraph::V(.)$superior * 7 + 7,
					 vertex.label = replace_names$sp_letter,
					 vertex.label.family = fam,
					 vertex.label.color = l_c,
					 vertex.label.font = igraph::V(.)$superior,
					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
					 # vertex.shape = igraph::V(.)$vertex.shape,
					 vertex.color = pal[igraph::V(.)$matched],
					 edge.color = pal[E(.)$matched],
					 edge.label = NA, 
					 edge.width = E(.)$matched/2,
					 edge.label.family = fam,
					 edge.label.color = igraph::E(.)$matched,
					 edge.label.cex = l_s,
					 edge.curved = F,
					 edge.arrow.size = 0.5,
					 margin = ma) %>% 
			print()

@@

		text(label_pos_x, label_pos_y, paste0(letters[2+x], ")"), adj = c(0,0))
		text(text_pos_x + 0.2, text_pos_y + 0.1, cex = 0.95,
				 paste0("D = ", length(igraph::V(as_net)) - as_mat$matching_size, "\n",
				 			 "matching size: ", as_mat$matching_size, "\n",
				 			 "matching weight: ", round(matching_weight, 1)))
})

@@

legend(0.28, 0.95, legend = replace_names$sp_name, horiz = F, bty = "n", text.font = 3, cex = 0.9)
legend(0.2, 0.95, legend = replace_names$sp_letter, horiz = F, bty = "n", text.font = 2, cex = 0.9)

@@

The studied networks had species richess ranging between `r min(net_prop$n_s_t)` and `r max(net_prop$n_s_t)` (`r min(net_prop$n_sp)`-`r max(net_prop$n_sp)` when considering only the largest component in each network). As evidenced by the overall network asymmetry *AS* [@Bluthgen2007] networks had a low ratio of plants to pollinators. Furthermore, networks had relatively low levels of nestedness [when measured using the quantitative version of the NODF index; @Almeida-Neto2011]. Details for each network can be found in Supporting Table 1.

@@

net_prop %>%
	dplyr::select(-net_name, -count, -net) %>%
	dplyr::filter(study != "ballantyne") %>%
	dplyr::arrange(study, site, inv) %>%
	mutate_cond(inv == FALSE, invader = "—") %>%
  dplyr::mutate(site = rep(1:dplyr::n_distinct(site), each = 2),
                inv = plyr::mapvalues(inv, c(TRUE, FALSE), c("yes", "no")),
                study = plyr::mapvalues(study, 
                                        c("bartomeus", "lopezaraiza"),
                                        c("Cap de Creus, Spain",
                                          "Bristol, United Kingdom"))) %>%
	dplyr::select(site, invader, n_s_t, n_sp, n_pla, n_pol, connectance, web.asymmetry, weighted.NODF, study) %>%
	dplyr::rename_("$R$" = "n_s_t",
								 "$n_p$" = "n_pla",
								 "$n_a$" = "n_pol",
								 "location" = "study",
								 "$n_s$" = "n_sp",
								 "$c$"= "connectance", 
								 "NODF" = "weighted.NODF",
								 # "$\\bar{a}$" = "interaction.strength.asymmetry",
								 "$AS$" = "web.asymmetry") %>%
	xtable::xtable(caption = "\\textbf{Properties of the analysed plant-pollinator communities}. Invasive plants were \\textit{Carpobrotus affine acinaciformis} (car), \\textit{Opuntia stricta} (op), and \\textit{Impatients grandulifera} (imp). All properties, with the exception of the networks' total species richness ($R$), correspond to the network's largest component. Specifically we show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network assymetry ($AS$), and the network nestedness (NODF index). British networks were assembled by Lopezaraiza-Mikel et al. (2007), Spanish were networks assembled by Bartomeus et al. (2008).") %>%
	print(#floating.environment = "sidewaystable", 
		comment = FALSE, sanitize.text.function = function(x){x}, include.rownames = FALSE)

@@

mapply(my_paste, correlations$r, correlations$P) %>%
  matrix(ncol = length(dir_net_b)) %>% magrittr::set_colnames(nam) %>%
  magrittr::set_rownames(nam) %>% `[<-`(lower.tri(.), lt) %>% 
  xtable::xtable(caption = "\\textbf{Agreement among network weighting schemes}. Spearman correlation coeffcients (with p-value) of specie's $f_D$ and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.") %>%
	print(comment = FALSE, include.rownames = TRUE)

@@

cowplot::plot_grid(p1, p2, ncol = 1, align = "v", rel_heights = c(1,1), labels = c("a)", "b)"), label_size = 8)

>>>>

---
title: "Biotic invasions fuck with the manageability of pollination networks"
subtitle: "Supporting Information"
classoption: a4paper
csl: ecology-letters.csl
output:
  pdf_document:
    fig_crop: no
    keep_tex: yes
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \renewcommand{\thefigure}{S\arabic{figure}}
- \renewcommand{\thetable}{S\arabic{table}}
- \usepackage[tableposition=top]{caption}
documentclass: artikel1
bibliography: references.bib
nocite: | 
  @Lopezaraiza-Mikel2007, @Bartomeus2008
---

@@

		igraph::E(bi_net)$matched_col <- 1
		igraph::E(bi_net)$matched_col[as_all_mat[[x]]] <- 5

@@

		igraph::V(bi_net)$matched_border <- 1
		igraph::V(bi_net)$matched_border[igraph::V(bi_net)$name %in%
																ends(bi_net, as_all_mat[[x]])[, 2]] <- 5

@@

		igraph::V(bi_net)$superior_shape <- "circle"
		igraph::V(bi_net)$superior_shape[igraph::V(bi_net)$name %in%
																ends(bi_net, as_all_mat[[x]])[, 1]] <- "square"

		names_fancy <- sp_names_fancy
		# names_fancy[igraph::V(bi_net)$name %in%
		# 														ends(bi_net, as_all_mat[[x]])[, 1]] <-
		# 	sp_names_fancy_b[igraph::V(bi_net)$name %in%
		# 														ends(bi_net, as_all_mat[[x]])[, 1]]

@@

We start with a directed network in which the direction of the link represents the direction of control (Figure S1a). We then construct an alternative representation of the directed network in which each node of the directed network is represented by two nodes that indicate their outgoing and incoming links (Figure S1b). Finding a maximum matching in this alternative representation is equivalent to finding the largest possible set of edges in which one node in the left hand side is connected to at most one node in the right hand side. To find the maximum matching we use the push-relabel algorithm implemented in `max_bipartite_matching` in the R package igraph 1.0.1 [@Csardi2006a]. Once we have the matching shown in the Figure S1b, it is then easy to identify the roles of each node in this representation: nodes on the right hand side that are connected to a matched link (purple) are matched, while those connected to a matched link on the left hand side are superior. This information can then be mapped back to the original representation to identify the control paths and the driver nodes in the network (Figure S1c). Figure S1d, e, and f ilustrate this approach for a network with bidirectional links.

@@

# par(mfrow=c(2,3), mar= c(0,0,0,0))
layout(matrix(c(1,2,3,4, 5, 6, 7, 7, 7), 3, 3, byrow = TRUE),
  	heights=c(8,8,2))
par( mar=c(0,0,0,0))
# ASYMMETRY
as_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 35,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma)

text(label_pos_x, label_pos_y, "(a)", adj = c(0,0), font = 2, cex = 0.9)

@@

igraph::E(bi_as_net)$matched_col <- 1
igraph::E(bi_as_net)$matched_col[as_all_mat[[1]]] <- 5

bi_as_net %>%
	plot(layout = matrix(c(rep(c(-0.5, 0.9), each = 5), rep(seq(-0.8, 0.8, length.out = 5), 2)), ncol = 2), 
			 # vertex.size = igraph::V(.)$superior,
			 vertex.size = 30, 
			 vertex.label = c(bi_sp_names_fancy[6:10], bi_sp_names_fancy[1:5]),
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 # vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
			 # vertex.color = pal[igraph::V(.)$matched],
			 vertex.color = NA,
			 edge.color = pal[E(.)$matched_col],
			 edge.label = NA, 
			 edge.width = E(.)$matched/2,
			 edge.label.family = fam,
			 edge.label.color = igraph::E(.)$matched,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma, 
			 rescale = F)

text(-0.95, 0.825, "(b)", adj = c(0,0), font = 2, cex = 0.9)

@@

E(as_net)$matched_col <- 1
E(as_net)$matched_col[as_all_mat[[1]]] <- 5

@@

igraph::V(as_net)$matched_border <- 1
igraph::V(as_net)$matched_border[igraph::V(as_net)$name %in%
														ends(as_net, as_all_mat[[1]])[, 2]] <- 5

@@

igraph::V(as_net)$superior_shape <- "circle"
igraph::V(as_net)$superior_shape[igraph::V(as_net)$name %in%
													 	ends(as_net, as_all_mat[[1]])[, 1]] <- "square"

names_fancy <- sp_names_fancy
# names_fancy[igraph::V(as_net)$name %in%
# 							ends(as_net, as_all_mat[[1]])[, 1]] <-
# 	sp_names_fancy_b[igraph::V(as_net)$name %in%
# 									 	ends(as_net, as_all_mat[[1]])[, 1]]

@@

as_net %>% 
	plot(layout = lay, 
			 vertex.size = 30,
			 vertex.shape = igraph::V(.)$superior_shape,
			 vertex.label = names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
			 # vertex.shape = igraph::V(.)$vertex.shape,
			 vertex.color = pal[igraph::V(.)$matched],
			 vertex.frame.color = pal[igraph::V(.)$matched_border],
			 edge.color = pal[E(.)$matched_col],
			 edge.label = NA, 
			 edge.width = E(.)$matched/2,
			 edge.label.family = fam,
			 edge.label.color = igraph::E(.)$matched,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma) %>% 
	print()

text(label_pos_x, label_pos_y, "(c)", adj = c(0,0), font = 2, cex = 0.9)

bi_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 35,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = T,
			 edge.arrow.size = 0.5,
			 margin = ma)
text(label_pos_x, label_pos_y, "(d)", adj = c(0,0), font = 2, cex = 0.9)

@@

igraph::E(bi_bi_net)$matched_col <- 1
igraph::E(bi_bi_net)$matched_col[nets[[i]]$as_all_mat] <- 5

@@

bi_bi_net %>%
	plot(layout = matrix(c(rep(c(0.9,-0.5), each = 5), rep(seq(-0.8, 0.8, length.out = 5), 2)), ncol = 2), 
			 # vertex.size = igraph::V(.)$superior,
			 vertex.size = 30,
			 vertex.label = bi_sp_names_fancy, 
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 # vertex.color = pal[igraph::V(.)$matched],
			 vertex.color = NA, 
			 edge.color = pal[igraph::E(.)$matched_col],
			 # edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.width = E(.)$matched/2,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin =  ma, 
			 # asp = 0.5, 
			 rescale = F)

text(-0.95, 0.825, "(e)", adj = c(0,0), font = 2, cex = 0.9)

nets[[1]]$bi_net %>%
	plot(layout = lay, 
			 vertex.label = nets[[1]]$names_fancy,
			 vertex.shape = igraph::V(.)$superior_shape,
			 vertex.size = 30,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 vertex.color = pal[igraph::V(.)$matched],
			 vertex.frame.color = pal[igraph::V(.)$matched_border],
			 edge.color = pal[igraph::E(.)$matched_col],
			 # edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = T,
			 edge.arrow.size = 0.5,
			 edge.width = E(.)$matched/2,
			 margin = ma, 
			 # asp = 0.5, 
			 rescale = T)

text(label_pos_x, label_pos_y, "(f)", adj = c(0,0), font = 2, cex = 0.9)

## LEGEND 
plot.new()
legend(0.55, 0.8, legend = c("unmatched link", "matched link"), horiz = TRUE,
			 lty = 1, 
			 col = pal[c(1, 5)],
			 lwd = 2, cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")

legend(0.89, 0.8, legend = c("unmatched node", "matched node"), horiz = TRUE,
			 pch = 21, 
			 pt.bg = pal[c(2, 4)],
			 col = pal[c(1,5)],
			 pt.cex = 2,
			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")

legend(0.7, 0.35, legend = c("superior node", "non-superior node"),
			 horiz = TRUE,
			 pch = c(22, 21), 
			 # pt.bg = pal[c(2, 4)],
			 pt.cex = 2,
			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")
```

The algorithm implemented in `max_bipartite_matching`, however, is only able to find **one** of the, possibly many, maximum matchings in a network. One maximum matching is sufficient to calculate *n~D~* and hence to provide indication of a communitie's manageability, however it is not possible to estimate the role of individual species. To do that we need to calculate all possible maximum matchings (or all maximal cardinality matchings in weighted networks like ours). We start from the alternative bipartite representation in Figure S1b and assign an identity to each of the links in the network (shown as numbers in Figure S2a). We will call this bipartite representation *B*. We then construct the line graph of the alternative bipartite representation *L(B)* (Figure S2b). Each node in *L(B)* represents a link in *B* and are connected to each other only if they share a common node in *B*. We calculate the complement graph of *L(B)* and idetify all the maximum cliques (Figure S2c). Here some extra definitions are neccessary. First, the complement of *L(B)*, *H*, is a graph with the same nodes as *L(B)* but that has a link between two given nodes if and only if there is not a link in *L(B)*. Second, a clique is a subset of nodes such that any two of them are linked. Lastly, a maximum clique is a clique such that there are no cliques with more nodes. In this example there are two maximum cliques: that one formed by 1, 3 and 5, and by 2, 3 and 5. The final step is then to map these cliques into the original network to obtain all possible maximum cardinality matchings as shown in Figure 1 in the main text.

@@

text(-1, 1, "(a)", adj = c(0,0), font = 2, cex = 0.9)

@@

text(-1, 1, "(b)", adj = c(0,0), font = 2, cex = 0.9)

@@

text(-1, 1, "(c)", adj = c(0,0), font = 2, cex = 0.9)

@@

In the main text we show all maximum cardinality matchings for a simple example network. To further ilustrate our methodology, here we also show the approach for the smallest of our empirical networks, the uninvaded network at site 10 (Table S1; Figure S3). The largest component of this network is composed by 16 species of which 2 are non-invasive plants and the rest are pollinators. The one-to-one relationship between matched and superior nodes implies that in order to achieve full network controllability, most pollinators would be unmatched, and hence driver species that require external intervention. At the same time, both plants in the community, *Heracleum sphpndylum* and *Rubus fructicosus* and one of the pollinators *Orthotylus/Lygocorus* tend to be classified as superior nodes.

```{r fig-SA_exp, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 6.2, results = "hide", fig.cap = "**Illustration of the procedure with one empirical network**. (a) The initial visitation network. (b) The directed network in which the direction of control and the magnitude of the asymmetry are determined based on the mutual dependences. (c) One of the possible maximum matchings calculated using the procedures illustrated in the Figure S1 and S2."}
par(mfrow=c(2,2), mar=c(0,0,0,0))
n <- keep_largest_component(net$SA_exp)
replace_names <- data.frame(sp_name = igraph::V(n)$name) %>%
	dplyr::mutate(sp_number = 1:nrow(.),
								sp_letter = letters[sp_number], 
								sp_name = stringr::str_replace(sp_name, "[0-9]", ""),
								sp_name = stringr::str_replace(sp_name, "\\?rutitarse", "rufitarse"))
set.seed(7)

la <- igraph::layout_nicely(n)
n %>%
	plot(vertex.color = v_c, 
			 vertex.size = 15,
			 vertex.label = replace_names$sp_letter,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 vertex.label.cex = 0.9,
			 edge.label = round(igraph::E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s*0.8,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma, 
			 layout = la)
text(label_pos_x, label_pos_y, paste0("(", letters[1], ")"), adj = c(0,0), font = 2, cex = 0.8)

@@

text(label_pos_x, label_pos_y, paste0("(", letters[2], ")"), adj = c(0,0), font = 2, cex = 0.8)

@@

		E(as_net)$matched_col <- 1
		E(as_net)$matched_col[as_all_mat[[x]]] <- 5

		igraph::V(as_net)$matched <- 2
		igraph::V(as_net)$matched[igraph::V(as_net)$name %in%
																ends(as_net, as_all_mat[[x]])[, 2]] <- 4
		igraph::V(as_net)$matched_border <- 1
		igraph::V(as_net)$matched_border[igraph::V(as_net)$name %in%
																ends(as_net, as_all_mat[[x]])[, 2]] <- 5

@@

		igraph::V(as_net)$superior_shape <- "circle"
		igraph::V(as_net)$superior_shape[igraph::V(as_net)$name %in%
																ends(as_net, as_all_mat[[x]])[, 1]] <- "square"

@@

		as_net %>% 
			plot(layout = la, 
					 vertex.size = 15,
					 vertex.label = replace_names$sp_letter,
					 vertex.shape = igraph::V(.)$superior_shape,
					 vertex.label.family = fam,
					 vertex.label.color = l_c,
					 vertex.label.font = igraph::V(.)$superior,
					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
					 # vertex.shape = igraph::V(.)$vertex.shape,
					 vertex.color = pal[igraph::V(.)$matched],
					 vertex.frame.color = pal[igraph::V(.)$matched_border],
					 edge.color = pal[E(.)$matched_col],
					 edge.label = NA, 
					 edge.width = E(.)$matched/2,
					 edge.label.family = fam,
					 edge.label.color = igraph::E(.)$matched_col,
					 edge.label.cex = l_s,
					 edge.curved = F,
					 edge.arrow.size = 0.5,
					 margin = ma) %>% 
			print()

@@

		text(label_pos_x, label_pos_y, paste0("(", letters[2+x], ")"), adj = c(0,0), font = 2, cex = 0.8)
		text(text_pos_x + 0.2, text_pos_y + 0.1, cex = 0.85,
				 paste0("D = ", length(igraph::V(as_net)) - as_mat$matching_size, "\n",
				 			 "matching size: ", as_mat$matching_size, "\n",
				 			 "matching weight: ", round(matching_weight, 1)))
})

@@

legend(0.28, 0.95, legend = replace_names$sp_name, horiz = F, bty = "n", text.font = 3, cex = 0.8)
legend(0.2, 0.95, legend = replace_names$sp_letter, horiz = F, bty = "n", text.font = 2, cex = 0.8)

@@

The studied networks had species richess ranging between `r min(net_prop$n_s_t)` and `r max(net_prop$n_s_t)` (`r min(net_prop$n_sp)`-`r max(net_prop$n_sp)` when considering only the largest component in each network). As evidenced by the overall network asymmetry *AS* [@Bluthgen2007] networks had a low ratio of plants to pollinators. Furthermore, networks had relatively low levels of nestedness [when measured using the quantitative version of the NODF index; @Almeida-Neto2011]. Details for each network can be found in Table S1.

@@

net_prop %>%
	dplyr::select(-net_name, -count, -net) %>%
	dplyr::filter(study != "ballantyne") %>%
	dplyr::arrange(study, site, inv) %>%
	mutate_cond(inv == FALSE, invader = "—") %>%
  dplyr::mutate(site = rep(1:dplyr::n_distinct(site), each = 2),
                inv = plyr::mapvalues(inv, c(TRUE, FALSE), c("yes", "no")),
                study = plyr::mapvalues(study, 
                                        c("bartomeus", "lopezaraiza"),
                                        c("Cap de Creus, Spain",
                                          "Bristol, United Kingdom"))) %>%
	dplyr::select(site, invader, n_s_t, n_sp, n_pla, n_pol, connectance, web.asymmetry, weighted.NODF, study) %>%
	dplyr::rename_("$R$" = "n_s_t",
								 "$n_p$" = "n_pla",
								 "$n_a$" = "n_pol",
								 "location" = "study",
								 "$n_s$" = "n_sp",
								 "$c$"= "connectance", 
								 "NODF" = "weighted.NODF",
								 # "$\\bar{a}$" = "interaction.strength.asymmetry",
								 "$AS$" = "web.asymmetry") %>%
	xtable::xtable(caption = "\\textbf{Properties of the analysed plant-pollinator communities}. Invasive plants were \\textit{Carpobrotus affine acinaciformis} (car), \\textit{Opuntia stricta} (op), and \\textit{Impatients grandulifera} (imp). All properties, with the exception of the networks' total species richness ($R$), correspond to the network's largest component. Specifically we show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network assymetry ($AS$), and the network nestedness (NODF index). British networks were assembled by Lopezaraiza-Mikel et al. (2007), Spanish were networks assembled by Bartomeus et al. (2008).") %>%
	print(#floating.environment = "sidewaystable", 
		comment = FALSE, sanitize.text.function = function(x){x}, include.rownames = FALSE, caption.placement = "top")

@@

mapply(my_paste, correlations$r, correlations$P) %>%
  matrix(ncol = length(dir_net_b)) %>% magrittr::set_colnames(nam) %>%
  magrittr::set_rownames(nam) %>% `[<-`(lower.tri(.), lt) %>% 
  xtable::xtable(caption = "\\textbf{Agreement among network weighting schemes}. Spearman correlation coeffcients (with p-value) of specie's $f_D$ and the percentage of interactions that share the direction of dependency obtained using the three weighting schemes and an unweighted scheme.") %>%
	print(comment = FALSE, include.rownames = TRUE, caption.placement = "top")

@@

cowplot::plot_grid(p1, p2, ncol = 1, align = "v", rel_heights = c(1,1), labels = c("(a)", "(b)"), label_size = 8)
